---
title: "Testing of BEST-COST R package"
author: "Alberto Castro & Axel Luyten"
output: html_document
---

# Preparation

The R script required the loading of certain R packages. 
```{r R script}
# Clear R environment
rm(list = ls())

# Load required packages
library(readxl)
library(dplyr)
library(tidyr)

library(ggplot2)
library(purrr)
library(stringr)
library(tibble)


library(zoo)
library(meta)

## To export tables in excel format
library(openxlsx)

## To load own packages
library(credentials)
library(gitcreds)
library(devtools)

```



```{r own packages}
# Install own package from github as suggested here
# https://stackoverflow.com/a/71846333/6104907
if(!"bestcost" %in% installed.packages()[, "Package"]){
  #gitcreds::gitcreds_set()
  credentials::set_github_pat()
  devtools::install_github(repo = "best-cost/best-cost_WPs",
                           subdir = "/r_package/bestcost",
                           force =TRUE)
}

library(bestcost)
```




```{r Useful variables}

#Decide 
# the target increment (increase of concentration) of the pm CRFs 
# and PM fraction
per_target_pm <- 10 # ug/m3

# Define existing PM fractions
pm_fractions <- c("PM2.5", "PM10")

# Set targeted PM fraction
pm_target <- "PM2.5"

# PM fraction that is not targeted
pm_no_target <- pm_fractions[!pm_fractions%in% pm_target]

# Pollutants to be considered in the hra based on available exposure data
pollutants_hra <- c(pm_target, "NO2")

# Define sex
sex <-  c("male", "female")

# Define values in the confidence interval (ci)
ci <- c("mean", "lowci", "highci")

# Define Outcome groups
groups <-
  data.frame(
    agegroup = c("below1", "from30"),
    outcome_group = c("infants", "adults")
  )

outcomeGroups <- groups$outcome_group

#IMPORTANT: Year to be run in the analysis air pollution HRA (health risk assessment)
# This should be one (or more than one) from the years_withData
# Change it as needed
year_hra <- "2019"

  

```


```{r Useful small functions}

# Create function to join mean CRF with the lower and upper bound
paste_CI <- 
  function(mean, low, high){
     paste0(mean," [", low, "; ", high, "]")
  }

# Create function to round keeping zeros in decimals (e.g. 2.0 instea of 2)
# We use sprintf() instead of round() because 
# the former keep the zeros unlike the latter
round_keeping0 <- 
  function(value, decimals){
    sprintf(paste0("%.", decimals, "f"), value)
  }
  
# Create function to round the values of the CRF and then paste
paste_round_CI <- 
  function(mean, low, high, decimals){
    paste0(round_keeping0(mean, decimals)," [",  
           round_keeping0(low, decimals), "; ", 
           round_keeping0(high, decimals), "]")
  }

```


# Input data


## Generic data
```{r Other generic data}

# Read single-value generic data
generic_data <- 
  read.csv("r_package/testing/input/generic_data.csv",
           sep = ";")

# Extract the value of the conversion factor from the generic_data csv file
percentage_pm2.5_in_pm10 <- 
  generic_data %>%
  dplyr::filter(parameter_name %in% "percentage_pm2.5_in_pm10") %>%
  dplyr::select(value)%>%
  dplyr::pull()


```


## CRFs data
```{r crf_rawdata}

# Read CRF data inserted manually in the csv table 
crf_rawdata <- 
  read.csv("r_package/testing/input/crf.csv",
           sep = ";",
           na.strings=c("NA", ""))



```



Concentration response functions (CRFs) had to be re-scaled in some cases so that all CRFs had the same unit, i.e. same PM fraction and same concentration increase (increment)


```{r pm_rescale} 
# Define function to re-scale the CRF regarding the considered increment
rescale_crf_increment <- 
  function(crf, per_original, per_target){
    rescaled_increment <- 
      exp(log(crf) * per_target / per_original)
  }

# Conversion factor for PM fraction
conversionFactor_pmFraction <-
  function(pm_original, pm_target){
    
    # Divide the percentage (%) by 100 to get the ratio (0.) 
    # And depending on the pm selected choose the default or the inverse form
    conversionfactor_ch <- 
      ifelse(pm_original %in% "PM2.5" &
               pm_target %in% "PM10",
             1/(percentage_pm2.5_in_pm10/100),
             ifelse(pm_original %in% "PM10" & 
                      pm_target %in% "PM2.5",
                    percentage_pm2.5_in_pm10/100,
                    1))
  }



```



```{r rescale concentration}

# Define function to re-scale the CRF regarding the considered PM fraction
rescale_conc_pmFraction <- 
  function(conc, pm_original, pm_target){
    
    # Divide the percentage (%) by 100 to get the ratio (0.) 
    # And depending on the pm selected choose the default or the inverse form
    conversionfactor_ch <- 
      conversionFactor_pmFraction(pm_original, pm_target)
    
    rescaled_fraction <- 
      conc * conversionfactor_ch
    
    return(rescaled_fraction)
  }
```



```{r crf_data rescaling crf}
crf_data <- 
  crf_rawdata%>%
  # Select only CRFs that are relevant for the project GeLuft
  dplyr::filter(!is.na(geluft_pair))%>%
  # Reshape from wide to long 
  tidyr::pivot_longer(c(crf_mean, crf_lowci, crf_highci),
                      names_to = "ci",
                      names_prefix = "crf_", 
                      values_to = "crf")%>%
  # Add columns with the original values (before re-scaling)
  dplyr::mutate(
    crf_pollutant_original = pollutant,
    crf_original = crf,
    crf_per_original = crf_per,
  # Add the CRF increment (increase of concentration) for each pollutant
    crf_per_target =
      ifelse(pollutant %in% c(pm_fractions, "NO2"), 10, NA),
      # ifelse(pollutant %in% "BC", 0.44, NA)))%>%
      # ifelse(pollutant %in% "O3", , NA))))%>% 
      # If O3 is included, the O3 increment is to be decided
  # Re-scale PM fractions in CRFs
    crf_per_rescaled = 
      rescale_conc_pmFraction(
        conc = crf_per_original,
        pm_original = crf_pollutant_original,
        pm_target = pm_target),
    crf_rescaled = 
      rescale_crf_increment(
        crf = crf,
        per_original = crf_per_rescaled,
        per_target = crf_per_target),
    crf = crf_rescaled)%>%
  
  # Modify columns based on target
  dplyr::mutate(
    pollutant = 
      ifelse(pollutant %in% pm_no_target, 
             pm_target, 
             crf_pollutant_original),
    crf_per = 
      ifelse(!crf_per %in% crf_per_target, 
             crf_per_target, 
             crf_per))%>%
  # Assume that if NA in multipollutant, it means single pollutant model
  dplyr::mutate(
    crf_model = 
      ifelse(crf_model %in% "multi-pollutant", 
             crf_model, 
             "single-pollutant"))%>%



  # Change format of source
  # Remove brackets and spaces
  dplyr::mutate(
    crf_source_rFormat = 
      paste(
        # First word
        stringr::word(crf_source, 1),
        # Year between brackets
        stringr::str_extract(crf_source, "(?<=\\().*(?=\\))"),
        sep = "_"))%>%
  
  # Add id for outcome as single variable
  tidyr::unite("outcome_id",
               outcome_metric, outcome_disease, outcome_group,
               na.rm = TRUE,
               remove = FALSE) %>%
  # Add id for outcome as single variable
  tidyr::unite("pair_id",
               pollutant, outcome_id, geluft_pair,
               na.rm = TRUE,
               remove = FALSE)%>% 
  # Add id for crf
  tidyr::unite("crf_id",
               pair_id, crf_source_rFormat, geluft_crf,
               sep = "_", 
               na.rm =TRUE,
               remove = FALSE)%>%
  # Keep only unique values
  dplyr::distinct(., crf_id, outcome_disease, 
                  crf, ci, 
                  .keep_all = TRUE)%>%
  # Change position of per columns
  dplyr::relocate(c(crf_per, concentration_unit), .after=crf)%>%
# pivot wider to have ci in columns
  tidyr::pivot_wider(values_from = c(crf, crf_original, crf_rescaled), 
                     names_from = ci)


```



```{r values based on crf table}
# Store the pollutant-outcomes pairs 
# that are considered in the main report or in the appendix of GeLuft
geluft_pairs_main <- 
  crf_data %>% dplyr::filter(geluft_pair %in% "main") %>% select(pair_id) %>% unique() %>% pull()
geluft_pairs_appendix <- 
  crf_data %>% dplyr::filter(geluft_pair %in% "appendix") %>% select(pair_id) %>% unique() %>% pull()

geluft_crf_all <- c(geluft_pairs_main, geluft_pairs_appendix)

geluft_crf_main_selected <- 
  crf_data %>% 
  dplyr::filter(pair_id %in% geluft_pairs_main & 
                  geluft_crf %in% "selected") %>% 
  select(crf_id) %>% unique() %>% pull()

geluft_crf_main_sensitivity <- 
  crf_data %>% 
  dplyr::filter(pair_id %in% geluft_pairs_main & 
                  geluft_crf %in% "sensitivity") %>% 
  select(crf_id) %>% unique() %>% pull()


geluftt_pairs <- c("main", "appendix")
geluft_crfs <- c("selected", "sensitivity")


```



```{r Subsets of crf data}

# Data in list form to be prepared for loops
crf_data_forLoop <-
  # Split (make list) by main/appendix, pollutant, oucome_id and selected/sensitivity
  split(crf_data, crf_data$geluft_pair)%>%
  purrr::map(function(x) split(x, x$pollutant))%>%
  purrr::map(map, function(x) split(x, x$outcome_id))%>%
  purrr::map(map, map, function(x) split(x, x$geluft_crf))  

# CRF data for all-cause mortality (removing disease specific)
crf_data_allCauseMortality <-
  dplyr::filter(crf_data,
    outcome_metric %in% "premature deaths" &
    outcome_disease %in% "all causes")

# CRF data for all-cause mortality (removing disease specific)
crf_data_allCauseMortality_adults <-
  dplyr::filter(crf_data_allCauseMortality,
    outcome_group %in% "adults")

crf_data_allCauseMortality_infants <-
  dplyr::filter(crf_data_allCauseMortality,
    outcome_disease %in% "infants")

crf_data_morbidities<- 
   dplyr::filter(crf_data,
    !outcome_metric %in% "premature deaths")



```






## Baseline health (morbidity) data
```{r bhd_data}

# Baseline health data 
bhd_rawdata <- 
  read.csv("r_package/testing/input/bhd.csv", sep = ";")

# Adapt the rawdata as needed
bhd_data <- 
  bhd_rawdata %>%
  # Remove the column hra
  dplyr::select(-hra) %>%
                  
  dplyr::mutate(
    # change format of year
    bhd_year = as.character(bhd_year),
    # Calculate the rate based on the absolute value
    # Already available in the csv but to be overwritten just in case that 
    # we forgot to update it there.
    bhd_rate = round(bhd_absolute / 86.06, 2))%>%
  #Add bhd_id
  tidyr::unite("outcome_id",
               outcome_metric, outcome_disease, outcome_group,
               sep = "_", 
               na.rm =TRUE,
               remove = FALSE)%>%
  #Filter the data to remove "all ages" in some of the GBD data
  dplyr::filter(!(source %in% "IHME (2020)" & 
                    outcome_disease %in% c("lung cancer",
                                           "ischemic heart disease",
                                           "stroke",
                                           "diabetes (type 2)",
                                           "dementia")&
                    age %in% "all"))

```


```{r subsets}
bhd_data_forLoop <- 
  bhd_data %>%
  # Split (make list) by id
  split(.$outcome_id)

bhd_data_morbidity <- bhd_data %>%
  # Keep only those rows that are relevant for GeLuft 
  # (only morbidity because mortality is to be done with life tables)
  dplyr::filter(!outcome_metric %in% "premature deaths")
```




## Population data 


```{r Population data by age for life table}
# Population data by age
# To be used in the life table approach
population_byAge_rawdata <-
  read.csv2("r_package/testing/input/population/population_byAge_bySex_CH_2018_2019.csv")%>%
  # Rename columns
  dplyr::rename("age" = "Alter",
                "male_end2018" = "Mann.2018",
                "female_end2018" = "Frau.2018",
                "male_end2019" = "Mann.2019",
                "female_end2019" = "Frau.2019")%>%
  # Remove "Jahre" 
    dplyr::mutate(
      age = gsub(" Jahre| Jahr","", age ))




# Create a list with two elements to split male and female data 
# (each of them requires a separate life table calculation)
population_byAge <- 
  list()

for (s in sex){
  population_byAge[[s]] <- 
    population_byAge_rawdata %>%
    # Select relevant columns
    dplyr::select(age, starts_with(s))%>%
    # Estimate the population at the middle of 2019 by 
    # calculating the average between the population at the end of 2018 and 2019
    dplyr::mutate(
      population = rowMeans(across(contains(s)), na.rm = TRUE))%>%
    # Remove male and female columns used to calculate the mean
    dplyr::select(-contains(s))%>%
    # Remove "und mehr" (and more)
    dplyr::mutate(
      age = gsub(" und mehr","", age ))
  
}





```



## Life table

```{r Probability of dying}

lifetable <- list()

# Read raw data
for(s in sex){
  # Life table for 2019
  # Average of the period 2016-2020
  lifetable[[s]] <- 
    read.csv2(
      # The raw data are for the period 2013-2020 but we focused on 2015-2019 (five years period)
      paste0("r_package/testing/input/life_tables/life_table_2013_2020_",
             s,
             ".csv"))%>%
    # Rename columns
    dplyr::rename("age" = "AGE..X." ,
                  "indicator" = "INDICATOR",
                  "year"  = "PERIOD",
                  "value" = "VALUE")%>%
    # Convert value to numeric
    dplyr::mutate(value = as.numeric(value))%>%
    # Filter only columns for years within the period 2015 - 2019
    dplyr::filter(year %in% c(2015:2019))%>%
    # Obtain mean of the period 2016-2020 as value for 2019
    dplyr::group_by(indicator, age)%>%
    dplyr::summarize(mean= mean(value), .groups = "drop")%>%
    # Wider form
    tidyr::pivot_wider(names_from = indicator, values_from = mean)%>%
    # Rename column probability of dying
    dplyr::rename("death_probability" = "Q(X)")%>%
    # Select columns probabilyt of dying (drop the other indicators)
    dplyr::select(age, death_probability)
    
  
}


for (s in sex){
  
    # Convert column age in lifetable to character 
    # to have the same type as in population data
    lifetable[[s]]$age <- 
      as.character(lifetable[[s]]$age)
  
}
```




```{r Mortality data}

nonNatural_mortality_rawdata <- list()
total_mortality_rawdata <- list()

nonNatural_mortality <-list()
total_mortality <- list()
# Create list joining non-natural and total mortality data
  mortality_data_beforeCorrecting <- list()
  mortality_data <- list()



# Read non-natural mortality raw data for 2019 (average of the period 2009-2019)
nonNatural_mortality_rawdata<- 
   list(
     male = read.csv2("r_package/testing/input/mortality/nonNatural_mortality_byAge_2009_2019_male.csv",
                      na.strings =".", 
                      check.names = FALSE),
     female = read.csv2("r_package/testing/input/mortality/nonNatural_mortality_byAge_2009_2019_female.csv",
                        na.strings =".", 
                      check.names = FALSE))

# Read total mortality raw data for 2019 (average of the period 2009-2019)
total_mortality_rawdata <- 
  list(
    male = read.csv2("r_package/testing/input/mortality/total_mortality_byAge_2009_2019_male.csv",
                     na.strings =".", 
                      check.names = FALSE),
    female = read.csv2("r_package/testing/input/mortality/total_mortality_byAge_2009_2019_female.csv",
                       na.strings =".", 
                      check.names = FALSE))

#Create a copy of rawdata to edit them
nonNatural_mortality <- 
      nonNatural_mortality_rawdata 
total_mortality <- 
      total_mortality_rawdata 
  
# Calculate average by age in non-natural and total mortality
for(s in sex){
    # Non-natural mortality
    nonNatural_mortality[[s]] <- 
      nonNatural_mortality[[s]] %>%
      # Select columns keeping only those 10 year before (2010-2019)
      dplyr::select(all_of(c("Age", as.character(2010:2019))))%>%
      # Calculate average by age
      dplyr::mutate(mean_nonNatural = 
                      rowMeans(subset(nonNatural_mortality[[s]], 
                                      select = -Age), 
                               na.rm = TRUE))
    
    # Total mortality
    total_mortality[[s]] <- 
      total_mortality[[s]] %>%
      # Select columns keeping only those 10 year before (2010-2019)
      dplyr::select(all_of(c("Age", as.character(2010:2019))))%>%
      # Calculate average by age
      dplyr::mutate(mean_total = 
                      rowMeans(subset(total_mortality[[s]], 
                                      select = -Age), 
                               na.rm = TRUE))
 
  mortality_data_beforeCorrecting[[s]] <-
    # Add row from non-natural mortality
    dplyr::left_join(total_mortality[[s]][, c("Age", "mean_total")],
                     nonNatural_mortality[[s]][, c("Age", "mean_nonNatural")],
                     by = "Age") %>%
    # Rename column Age to age %>%
    dplyr::rename("age" = "Age")%>%
    # Calculate percentage of deaths from non-natural mortality
    dplyr::mutate(percent_nonNatural_raw = mean_nonNatural / mean_total)
    
    
    
    # Calculate the moving average (mean of 5 ages) to correct yearly deviations
  mortality_data[[s]] <-
    mortality_data_beforeCorrecting[[s]]%>%
    dplyr::mutate(percent_nonNatural_movingAverage = 
                    zoo::rollmean(percent_nonNatural_raw, 
                                  k = 5, 
                                  fill = NA))%>%
    # The three first lines of the moving average are special cases
    # Edit them manually
    dplyr::mutate(percent_nonNatural = 
                    ifelse(age == 0, percent_nonNatural_raw,
                           ifelse(age == 1, mean(percent_nonNatural_raw[2:4], 
                                                 na.rm =TRUE),
                                  ifelse(age == 2, mean(percent_nonNatural_raw[2:5],
                                                        na.rm =TRUE),
                                         percent_nonNatural_movingAverage))))%>%
    # Keep only age and percentage of non-natural deaths, which the only data needed.
    dplyr::select(age, percent_nonNatural)
    
  
}

```




```{r get_lifetable_withPopulation}

get_lifetable_withPopulation <-
  function(lifetable, population, firstYear_lifetable){
        
    
    # Life table for 
    lifetable_withPopulation <- 
      # Join lifetable and population by age 
      dplyr::right_join(lifetable,
                        population,
                        by = "age")%>%
      # We close the last row assigning a 1 for probability to die and 
      # a 0 to probability to survive
      dplyr::mutate(death_probability = replace(death_probability, n(), 1))%>%
      # Add year to population column
      dplyr::rename("population_{firstYear_lifetable}" := population)
      
  }
```



```{r lifetable_withPopulation}

lifetable_withPopulation <- list()

for(s in sex){
  lifetable_withPopulation[[s]] <-
    get_lifetable_withPopulation(
      lifetable = lifetable[[s]],
      population = population_byAge[[s]],
      firstYear_lifetable = 2019)

}


```





## Concentration data


```{r exposure}

# Select relevant columns
exp_rawdata <- 
  read.csv("r_package/testing/input/exp.csv",
           sep = ";",
           na.strings=c("NA", ""))


# This data set will include other data beyond those from HRAs
exp_data <- 
  exp_rawdata%>%
  # Remove url colum
  dplyr::select(-url, -hra, -estimation)%>%
  # Remove the columns for lower and upper bound of the concentration 
  # (not relevant for the project GeLuft)
  dplyr::select(-concentration_exp_lowci, -concentration_exp_highci)%>%
  # Rename concentration column
  dplyr::rename(exp = concentration_exp_mean)%>%
  # Filter keeping only relevant rows for the project GeLuft
  dplyr::filter(concentration_year %in% c("2019", "lrv", "whoaqg21"))%>%
  # Add columns with the original values (before re-scaling)
  dplyr::mutate(
    pollutant_original = pollutant,
    exp_original = exp,
    # Modify columns pollutant
    pollutant = 
      ifelse(pollutant %in% pm_no_target, 
             pm_target, 
             pollutant_original))%>%
  # Convert the exposure
  dplyr::mutate(
    exp = 
      rescale_conc_pmFraction(
        conc = exp_original,
        pm_original = pollutant_original,
        pm_target = pm_target))


  
```


```{r Subsets}
# Exposure data in a list form
exp_data_forLoop <- 
  exp_data %>%
  # Split (make list) by pollutant and year
  split(.$pollutant)%>%
  purrr::map(function(x) split(x, x$concentration_year))
  


```


```{r table to export}

exp_data_swiss_xls<- 
  exp_data %>%
  dplyr::arrange(desc(pollutant), exp) %>%
  dplyr::mutate(exp = round(exp, 3))



```


```{r Counterfactual scenario}

cf_data <-
  exp_data %>%
  # Take the WHO-AQG 2021 
  dplyr::filter(concentration_year %in% "whoaqg21") %>%
  dplyr::select(pollutant, exp)%>%
  # Rename the column
  dplyr::rename(cf =exp)

```



# Calculating health impacts

```{r Codebook}

# Do not forget yll
codebook <- unique(bhd_data[, c("outcome_id", "outcome_label_de", "mort_morb")]) %>%
  # Add label for crf
  # replacing premature deaths / yll by mortality
  mutate(crf_label_de = ifelse(outcome_id %in% c("premature deaths_all causes_adults", "yll_all causes_adults"),
                               "Krankheitsbedingte Sterblichkeit bei Erwachsenen",
                               ifelse(outcome_id %in% c("premature deaths_all causes_infants", "yll_all causes_infants"),
                                      "Säuglingssterblichkeit",
                                      outcome_label_de)))

```



```{r input data}
input_data <-
  
  # Join data sets of input data
  dplyr::left_join(exp_data, crf_data, by="pollutant", 
                   suffix =c("_exp", "_crf"),
                   relationship = "many-to-many")%>%
  dplyr::left_join(., bhd_data, by="outcome_id",
                   suffix = c("", "_bhd"),
                   relationship = "many-to-many")%>%
  # Add counterfactual
  dplyr::left_join(., cf_data, by="pollutant",
                   relationship = "many-to-one")

input_data_morbidities <- 
  input_data %>%
  dplyr::filter(crf_id %in% crf_data_morbidities$crf_id)

input_data_mortality <- 
  input_data %>%
  dplyr::filter(crf_id %in% crf_data_allCauseMortality$crf_id)
```


```{r morbidities}
impact_morbidities_raw <- list()

for(i in 1:nrow(input_data_morbidities)){
  impact_morbidities_raw[[input_data_morbidities$concentration_year[i]]][[input_data_morbidities$crf_id[[i]]]] <-
  healthiar::calculate_healthImpacts(
    exp = input_data_morbidities$exp[i],
    cf = input_data_morbidities$cf[i],
    bhd = input_data_morbidities$bhd_absolute[i],
    crf = unlist(input_data_morbidities[i, 
                            c("crf_mean", "crf_lowci", "crf_highci")]) ,
    crf_per = 10, 
    crf_rescale_method = "loglinear", 
    pollutant = input_data_morbidities$pollutant[i], 
    outcome_metric = input_data_morbidities$outcome_metric[i], 
    age_group = input_data_morbidities$outcome_group[i])
      
}

impact_morbidities_edited <- 
  # Bind rows within the nested lists
  impact_morbidities_raw %>%
  purrr::map(., ~ dplyr::bind_rows(., .id = "crf_id")) 

impact_morbidities_comparative <- list()
for (r in c("2019", "lrv")){
  
  # Substract the impacts for the scenarios
  impact_morbidities_comparative[[paste0(r, "_whoaqg21")]] <- 
    dplyr::left_join(impact_morbidities_edited[[r]],
                     impact_morbidities_edited[["whoaqg21"]][c("crf_id", "ci", "crf", "exp", "impact")], 
                     by = c("crf_id", "ci", "crf"), 
                     suffix = c("_ref", "_whoaqg21"))%>%
    dplyr::mutate(ref = r,
                  impact_diff = impact_ref - impact_whoaqg21)
  }

impact_morbidities <- 
  impact_morbidities_comparative %>%
  dplyr::bind_rows(.)%>%
  # Remove column crf_ci
  dplyr::select(-crf_ci, -crfConc, -af)%>%
  
  # Pivot wider the ci
  tidyr::pivot_wider(
    values_from = c(crf,
                    impact_ref, impact_whoaqg21, impact_diff), 
    names_from = ci)%>%
  # Paste the CIs
  dplyr::mutate(
    crf_meanCI = paste_round_CI(crf_mean, crf_lowci, crf_highci, 3),
    impact_ref_meanCI = paste_round_CI(impact_ref_mean, impact_ref_lowci, impact_ref_highci, 0),
    impact_whoaqg21_meanCI = paste_round_CI(impact_whoaqg21_mean, impact_whoaqg21_lowci, impact_whoaqg21_highci, 0),
    impact_diff_meanCI = paste_round_CI(impact_diff_mean, impact_diff_lowci, impact_diff_highci, 0))%>%
  
      # Pivot wider the impacts
  tidyr::pivot_wider(
    values_from = 
      c(contains("_ref"),contains("_diff")),
    names_from = ref)%>%
  
    # Left join to add further information on crf
  dplyr::left_join(., crf_data, 
                   by = c("pollutant", "crf_id", 
                          paste0("crf_", c("mean", "lowci", "highci"))),
                   relationship = "many-to-one")%>%
     # Left join to add further information on bhd
  dplyr::left_join(., unique(input_data_morbidities [, c("outcome_id", "bhd_absolute", "source_bhd", "geluft_bhd")]), 
                   by = c("outcome_id", "bhd" = "bhd_absolute"),
                   relationship = "many-to-one")%>%
  # Left join to add label in German of outcomes
  dplyr::left_join(., codebook, 
                   by = "outcome_id",
                   relationship = "many-to-one")%>%
  
  # Order columns 
  dplyr::select(pollutant, term, outcome_label_de,
                bhd,
                crf_meanCI, 
                contains("impact_diff_meanCI"),
                contains("impact_ref_meanCI"), 
                impact_whoaqg21_meanCI,
                everything())%>%
  # Order rows by label
  dplyr::arrange(outcome_label_de)



```



```{r mortality}
impact_mortality_raw <- list()

# Calculate using healthiar

for(i in 1:nrow(input_data_mortality)){
  impact_mortality_raw[[input_data_mortality$concentration_year[i]]][[input_data_mortality$crf_id[[i]]]] <-
  healthiar::calculate_mortality_usingLifetable(
    exp = input_data_mortality$exp[i],
    cf = input_data_morbidities$cf[i],
    crf = unlist(input_data_mortality[i, 
                            c("crf_mean", "crf_lowci", "crf_highci")]) ,
    crf_per = 10, 
    crf_rescale_method = "loglinear", 
    lifetable_withPop_male = lifetable_withPopulation[["male"]],
    lifetable_withPop_female = lifetable_withPopulation[["female"]],
    firstYear_lifetable = 2019, 
    nonNatural_death_male = mortality_data[["male"]],
    nonNatural_death_female = mortality_data[["female"]], 
    pollutant = input_data_mortality$pollutant[i], 
    age_group = input_data_mortality$outcome_group[i],
    min_age = 20,
    max_age = 0,
    corrected_discount_rate = 0)

}

impact_mortality_edited <- list()

impact_mortality_edited[["deaths"]] <- 
  # Extract only nested  lists with the name "deaths"  
  purrr::map_depth(impact_mortality_raw, 2, "deaths")
# Same with "yll"  
impact_mortality_edited[["yll"]] <- 
  purrr::map_depth(impact_mortality_raw, 2, "yll")

impact_mortality_edited <- impact_mortality_edited %>%
  # Unlist assigning id
  purrr::map(., map,  ~ dplyr::bind_rows(., .id = "crf_id"))%>%
  purrr::map(.,  ~ dplyr::bind_rows(., .id = "case"))%>%
  dplyr::bind_rows(., .id = "outcome_metric_short")%>%
  # Now list only scenario
  split(., .$case)

# Put together the different scenarios
impact_mortality_comparative <- list()
for (r in c("2019", "lrv")){
  # Substract the impacts for the scenarios
  impact_mortality_comparative[[paste0(r, "_whoaqg21")]] <- 
    dplyr::left_join(impact_mortality_edited[[r]],
                     impact_mortality_edited[["whoaqg21"]][c("crf_id", "ci", "impact", "outcome_metric_short", "exp")], 
                     by = c("outcome_metric_short", "crf_id", "ci"), 
                     suffix = c("_ref", "_whoaqg21"))%>%
    dplyr::mutate(ref = r,
                  impact_diff = impact_ref - impact_whoaqg21)
  }


impact_mortality <- 
  impact_mortality_comparative %>%
  dplyr::bind_rows(.)%>%
  # Remove non relevant columns
  dplyr::select(-impact_per_unit, -case)%>%
  
  # Pivot wider CI
  tidyr::pivot_wider(
    values_from = c(crf, 
                    impact_ref, impact_whoaqg21, impact_diff), 
    names_from = ci)%>%
  # Paste the CIs
  dplyr::mutate(
    crf_meanCI = paste_round_CI(crf_mean, crf_lowci, crf_highci, 3),
    impact_ref_meanCI = paste_round_CI(impact_ref_mean, impact_ref_lowci, impact_ref_highci, 3),
    impact_whoaqg21_meanCI = paste_round_CI(impact_whoaqg21_mean, impact_whoaqg21_lowci, impact_whoaqg21_highci, 0),
    impact_diff_meanCI = paste_round_CI(impact_diff_mean, impact_diff_lowci, impact_diff_highci, 0),
    # bhd as NA just to match with structure of morbidities
    bhd = NA)%>%
  
  # Pivot wider the impacts
  tidyr::pivot_wider(
    values_from = 
      c(contains("_ref"),contains("_diff")),
    names_from = ref)%>%
    
  # Left join to add further information on crf
  dplyr::left_join(., crf_data, 
                   by = c("pollutant", "crf_id", "outcome_group",
                          paste0("crf_", c("mean", "lowci", "highci"))),
                   relationship = "many-to-one")%>%
     # Left join to add further information on geluft_bhd
  # Since there is a life table and no alternative 
  # the information has to be added manually
  dplyr::mutate(geluft_bhd = "selected") %>%
  
  # Change outcome_id to ensure match with codebook
  dplyr::mutate(
    outcome_id = ifelse(outcome_metric_short %in% "yll",
                        gsub("premature deaths", "yll", outcome_id),
                        outcome_id))%>%
  # Left join to add label in German of outcomes
  dplyr::left_join(., codebook, 
                   by = "outcome_id",
                   relationship = "many-to-one")%>%
  # Order columns 
  dplyr::select(pollutant, term,
                outcome_label_de,
                bhd,
                crf_meanCI, 
                contains("impact_diff_meanCI"),
                contains("impact_ref_meanCI"), 
                impact_whoaqg21_meanCI,
                everything())%>%
  # Order rows by label
  dplyr::arrange(outcome_group)


```

