---
title: "Testing of BEST-COST R package"
author: "Alberto Castro & Axel Luyten"
output: html_document
---
# Goal
Recreate calculation of AirQ+ with {bestcost}. For this, all necessary input data is loaded and manipulated to fit the required formats of {bestcost}. Then, the health impacts are calculated.

Pending
- Create table comparing the AirQ+ and bestcost results to always control that we do not deviate.
- Compare morbidity (not only mortality)
- healthiar vs. geluft in the package
- test

# Load packages and data


The R script required the loading of certain R packages. 
```{r Load packages, include=FALSE}
# Load required packages

# to assess performance
library(profvis)
library(bench)
library(microbenchmark)

# to manipulate data
library(readxl)
library(dplyr)
library(tidyr)
library(purrr)
library(stringr)
library(tibble)
library(zoo)

# to visualize results
library(ggplot2)

## to export tables in excel format
library(openxlsx)

## to load own packages
library(credentials)
library(gitcreds)
library(devtools)
```

```{r Install own package from github, eval=FALSE, include=FALSE}
# Install own package from github as suggested here: https://stackoverflow.com/a/71846333/6104907
if(!"bestcost" %in% installed.packages()[, "Package"]){
  #gitcreds::gitcreds_set()
  #usethis::use_git_config(user.name = "YourName", user.email = "your@mail.com") # run if installation doesn't work
  credentials::set_github_pat() # paste github PAT if prompted
  devtools::install_github(repo = "best-cost/best-cost_WPs",
                           subdir = "/r_package/bestcost",
                           ref = "paf_pif", # Branch name (by default "HEAD") as a string
                           force = TRUE)
}
library(bestcost)
```


```{r load bestcost package}
# Load package (either current version or installed version)
devtools::load_all(export_all = FALSE)
library(bestcost)
```



```{r load current version of bestcost from local source, eval=FALSE, include=FALSE}
detach("package:bestcost", unload = TRUE) # detach bestcost
devtools::build(binary = TRUE, path = "../testing/input/") # Save current state of package as .zip file (e.g. to directly test changes in functions)
install.packages("../testing/input/bestcost_0.0.0.1.zip", repos=NULL, type='source') # Install package from source
library(bestcost)
```


Load the Rdata file that contains all variables needed to run this script.
```{r load data }
load("../testing/input/input_data_for_testing_Rpackage.RData")
```


# Calculate health impacts

## Attributable health impact

```{r Test attribute_yld_rr single input value, eval=FALSE, include=FALSE}
test <- bestcost::attribute_yld_rr(
  dw = 0.133, # for health state "Asthma, uncontrolled" (cf. bestcost::disability_weights)
  exp = c(input_data_morbidities$exp[12], input_data_morbidities$exp[12]+20, input_data_morbidities$exp[12]+30),
  prop_pop_exp = c(0.2, 0.2, 0.6),
  cutoff = input_data_morbidities$cutoff[12],    # PM2.5=5, NO2=10, i.e. WHO AQG 2021 
  bhd = input_data_morbidities$bhd_absolute[12],
  rr = unlist(input_data_morbidities[12, c("rr_mean", "rr_lowci", "rr_highci")]), # RR for asthma incidence for adults
  rr_increment = 10, 
  erf_shape = "log_linear", 
  info_pollutant = input_data_morbidities$pollutant[12], 
  info_outcome = input_data_morbidities$outcome_metric[12]
)


# Ref 2783  583 4719 
# Ref * 0.133: 370  78  628
```

```{r Test probability of dying}
# Use function
prob_dying_airqplus <- 
  bestcost::get_prob_dying(
    first_age_pop = 0,
    last_age_pop = 14,
    interval_age_pop = 5,
    population_midyear = airqplus_deaths_pop_multipleYear$mi,
    deaths = airqplus_deaths_pop_multipleYear$di,
    fraction_of_year_lived = 0.5
  )
```

```{r absolute risk}

impact_annoyance_expDistribution_raw <- 
  bestcost::attribute_health_singlebhd_ar(
    exp = c(57.5, 62.5, 67.5, 72.5, 77.5),# Values as example provided by NIPH
    pop_exp = c(387500, 286000, 191800, 72200, 7700), # Values as example provided by NIPH
    erf_c = "78.9270-3.1162*c+0.0342*c^2",
    info = data.frame(pollutant = "road_noise", outcome = "highly_annoyance"))
```

```{r morbidity using exposure distribution}

impact_morbidity_expDistribution_raw <- list()

for(i in 1:nrow(input_data_morbidities)){
  impact_morbidity_expDistribution_raw[[input_data_morbidities$year[i]]][[input_data_morbidities$rr_id[[i]]]] <-
  bestcost::attribute_health_singlebhd_rr(
    exp = c(53, 57.5, 62.5, 67.5, 72.5, 77.5),# Values as example provided by NIPH
    prop_pop_exp = c(0.8187, 0.0743, 0.0549, 0.0368, 0.0138, 0.0015), # Values as example provided by NIPH
    cutoff = 53, # PM2.5=5, NO2=10, i.e. WHO AQG 2021 
    bhd = 5269.46,
    rr = c(1.08, 1.07, 1.09),
    rr_increment = 10, 
    erf_shape = "log_linear",
    info = data.frame(pollutant = "road_noise", outcome = "YLD"))
  }
```

```{r impact morbidity}
impact_morbidities_raw <- list()

#for(i in 1:nrow(input_data_morbidities)){
for(i in 12){ # runs loop only for HO "asthma incidence 20+"
  impact_morbidities_raw[[input_data_morbidities$year[i]]][[input_data_morbidities$rr_id[[i]]]] <-
  bestcost::attribute_health_singlebhd_rr(
    #dw = 0.133, # for health state "Asthma, uncontrolled" (cf. bestcost::disability_weights)
    exp = input_data_morbidities$exp[i],  # PM2.5=8.30=limit LRV CH, NO2=16.32=mean conc. in CH in 2019
    cutoff = input_data_morbidities$cutoff[i],    # PM2.5=5, NO2=10, i.e. WHO AQG 2021 
    bhd = input_data_morbidities$bhd_absolute[i],
    rr = unlist(input_data_morbidities[i, 
                            c("rr_mean", "rr_lowci", "rr_highci")]),
    rr_increment = 10, 
    erf_shape = "log_linear", 
    info = data.frame(pollutant = input_data_morbidities$pollutant[i], 
                      outcome = input_data_morbidities$outcome_metric[i]))
  }



```

```{r morbidity yld lifetable}
yld <- attribute_yld_lifetable_rr(
  exp = input_data_mortality$exp[2],
  # exp = c(8, 9, 10), # Fake data just for testing purposes
  prop_pop_exp = 1,
  # prop_pop_exp = c(0.2, 0.3, 0.5), # Fake data just for testing purposes
  cutoff = input_data_mortality$cutoff[2],
  rr = unlist(input_data_mortality[2, c("rr_mean", "rr_lowci", "rr_highci")]),
  rr_increment = 10, 
  erf_shape = "log_linear",
  first_age_pop = 0,last_age_pop = 99,
  interval_age_pop = 1,
  prob_natural_death_male = lifetable_withPopulation[["male"]]$death_probability_natural,
  prob_natural_death_female = lifetable_withPopulation[["female"]]$death_probability_natural,
  prob_total_death_male = lifetable_withPopulation[["male"]]$death_probability_total,
  prob_total_death_female = lifetable_withPopulation[["female"]]$death_probability_total,
  population_male = lifetable_withPopulation[["male"]]$population, 
  population_female = lifetable_withPopulation[["female"]]$population,
  year_of_analysis = 2019, 
  info = input_data_mortality$pollutant[2], 
  min_age = 20,
  # min_age = input_data_mortality$min_age[2],
  # min_age = NA,
  max_age = 99,
  # max_age = input_data_mortality$max_age[2],
  # max_age = NA,
  corrected_discount_rate = 0,
  duration = 2,
  disability_weight = 1
  )

print(paste("YLD", head(yld$total$impact_rounded)))
print("YLL (not discounted, as comparison) 40541.98 14640.90 27741.97")

impact_yll_expDistribution_raw <- list()
impact_yll_expDistribution_raw[[input_data_mortality$year[2]]][[input_data_mortality$rr_id[[2]]]] <-
    bestcost::attribute_yll_lifetable_rr(
      exp = input_data_mortality$exp[2],
      # exp = c(8, 9, 10), # Fake data just for testing purposes
      prop_pop_exp = 1,
      # prop_pop_exp = c(0.2, 0.3, 0.5), # Fake data just for testing purposes
      cutoff = input_data_mortality$cutoff[2], # WHO AQG 2021 
      rr = unlist(input_data_mortality[2, c("rr_mean", "rr_lowci", "rr_highci")]),
      rr_increment = 10, 
      erf_shape = "log_linear",
      first_age_pop = 0,
      last_age_pop = 99,
      interval_age_pop = 1,
      prob_natural_death_male = lifetable_withPopulation[["male"]]$death_probability_natural,
      prob_natural_death_female = lifetable_withPopulation[["female"]]$death_probability_natural,
      prob_total_death_male = lifetable_withPopulation[["male"]]$death_probability_total,
      prob_total_death_female = lifetable_withPopulation[["female"]]$death_probability_total,
      population_male = lifetable_withPopulation[["male"]]$population, 
      population_female = lifetable_withPopulation[["female"]]$population, 
      year_of_analysis = 2019, 
      info = input_data_mortality$pollutant[2], 
      min_age = if(is.na(input_data_mortality$min_age[2])) NULL else input_data_mortality$min_age[2],
      max_age = 99)
      #max_age = if(is.na(input_data_mortality$max_age[2])) NULL else input_data_mortality$max_age[2])

head(impact_yll_expDistribution_raw$`2019`$`PM2.5_premature deaths_all causes_adults_main_ERS-ISEE_2022_selected`$total$impact)
```


```{r mortality using exposure distribution}
impact_deaths_expDistribution_raw <- list()

# Calculate mortality impacts using bestcost function

#for(i in 1:nrow(input_data_mortality)){  # Use this if you want to evaluate multiple RRs
for(i in 2){                           # Use this if you want to evaluate only one RR
  impact_deaths_expDistribution_raw[[input_data_mortality$year[i]]][[input_data_mortality$rr_id[[i]]]] <-
    
    bestcost::attribute_deaths_lifetable_rr(
      exp = c(8, 9, 10), # Fake data just for testing purposes
      prop_pop_exp = c(0.2, 0.3, 0.5), # Fake data just for testing purposes
      cutoff = input_data_mortality$cutoff[i],   # PM2.5=5, NO2=10, i.e. WHO AQG 2021 
      rr = unlist(input_data_mortality[i,
                                        c("rr_mean", "rr_lowci", "rr_highci")]),
      rr_increment = 10, 
      erf_shape = "log_linear",
      first_age_pop = 0,
      last_age_pop = 99,
      interval_age_pop = 1,
      prob_natural_death_male = lifetable_withPopulation[["male"]]$death_probability_natural,
      prob_natural_death_female = lifetable_withPopulation[["female"]]$death_probability_natural,
      prob_total_death_male = lifetable_withPopulation[["male"]]$death_probability_total,
      prob_total_death_female = lifetable_withPopulation[["female"]]$death_probability_total,
      population_male = lifetable_withPopulation[["male"]]$population, 
      population_female = lifetable_withPopulation[["female"]]$population, 
      year_of_analysis = 2019, 
      info = input_data_mortality$pollutant[i], 
      min_age = if(is.na(input_data_mortality$min_age[i])) NULL else input_data_mortality$min_age[i],
      max_age = 99)
      # max_age = if(is.na(input_data_mortality$max_age[i])) NULL else input_data_mortality$max_age[i])

}

head(impact_deaths_expDistribution_raw$`2019`$`PM2.5_premature deaths_all causes_adults_main_ERS-ISEE_2022_selected`$total$impact) # to check results stay the same
#4250 1537 2911


impact_yll_expDistribution_raw <- list()

# Calculate mortality impacts using bestcost function

#for(i in 1:nrow(input_data_mortality)){  # Use this if you want to evaluate multiple RRs
for(i in 2){                           # Use this if you want to evaluate only one RR
  impact_yll_expDistribution_raw[[input_data_mortality$year[i]]][[input_data_mortality$rr_id[[i]]]] <-
    
    bestcost::attribute_yll_lifetable_rr(
      exp = c(8, 9, 10), # Fake data just for testing purposes
      prop_pop_exp = c(0.2, 0.3, 0.5), # Fake data just for testing purposes
      cutoff = input_data_mortality$cutoff[i], # WHO AQG 2021 
      rr = unlist(input_data_mortality[i, c("rr_mean", "rr_lowci", "rr_highci")]),
      rr_increment = 10, 
      erf_shape = "log_linear",
      first_age_pop = 0,
      last_age_pop = 99,
      interval_age_pop = 1,
      prob_natural_death_male = lifetable_withPopulation[["male"]]$death_probability_natural,
      prob_natural_death_female = lifetable_withPopulation[["female"]]$death_probability_natural,
      prob_total_death_male = lifetable_withPopulation[["male"]]$death_probability_total,
      prob_total_death_female = lifetable_withPopulation[["female"]]$death_probability_total,
      population_male = lifetable_withPopulation[["male"]]$population, 
      population_female = lifetable_withPopulation[["female"]]$population, 
      year_of_analysis = 2019, 
      info = input_data_mortality$pollutant[i], 
      min_age = if(is.na(input_data_mortality$min_age[i])) NULL else input_data_mortality$min_age[i],
      max_age = 99)
      #max_age = if(is.na(input_data_mortality$max_age[i])) NULL else input_data_mortality$max_age[i])
}
head(impact_yll_expDistribution_raw$`2019`$`PM2.5_premature deaths_all causes_adults_main_ERS-ISEE_2022_selected`$total$impact) 

```

```{r impact mortality}
# Calculate mortality impacts using bestcost function

impact_mortality_raw <- list()
#for(i in 1:nrow(input_data_mortality)){  # Use this if you want to evaluate multiple RRs
for(i in 2){                           # Use this if you want to evaluate only one RRs
  impact_mortality_raw[[input_data_mortality$year[i]]][[input_data_mortality$rr_id[[i]]]] <-
  
    bestcost::attribute_deaths_lifetable_rr(

    exp = input_data_mortality$exp[i], # PM2.5=8.30=limit LRV CH, NO2=16.32=mean conc. in CH in 2019
    cutoff = input_data_mortality$cutoff[i],   # PM2.5=5, NO2=10, i.e. WHO AQG 2021 
    rr = unlist(input_data_mortality[i,
                                      c("rr_mean", "rr_lowci", "rr_highci")]),
    rr_increment = 10, 
    erf_shape = "log_linear",
    first_age_pop = 0,
    last_age_pop = 99,
    interval_age_pop = 1,
    prob_natural_death_male = lifetable_withPopulation[["male"]]$death_probability_natural,
    prob_natural_death_female = lifetable_withPopulation[["female"]]$death_probability_natural,
    prob_total_death_male = lifetable_withPopulation[["male"]]$death_probability_total,
    prob_total_death_female = lifetable_withPopulation[["female"]]$death_probability_total,
    population_male = lifetable_withPopulation[["male"]]$population, 
    population_female = lifetable_withPopulation[["female"]]$population, 
    year_of_analysis = 2019, 
    info = input_data_mortality$pollutant[i], 
    min_age = input_data_mortality$min_age[i],
    max_age = 99)
    #max_age = input_data_mortality$max_age[i])
}

head(impact_mortality_raw[["2019"]][["PM2.5_premature deaths_all causes_adults_main_ERS-ISEE_2022_selected"]][["total"]]$impact)

# impact_mortality_edited <- list()
# 
# impact_mortality_edited[["deaths"]] <- 
#   # Extract only nested  lists with the name "deaths"  
#   purrr::map_depth(impact_mortality_raw, 2, "deaths")
# # Same with "yll"  
# impact_mortality_edited[["yll"]] <- 
#   purrr::map_depth(impact_mortality_raw, 2, "yll")
# 
# impact_mortality_edited <- impact_mortality_edited %>%
#   # Unlist assigning id
#   purrr::map(., map,  ~ dplyr::bind_rows(., .id = "rr_id")) %>%
#   purrr::map(.,  ~ dplyr::bind_rows(., .id = "case")) %>%
#   dplyr::bind_rows(., .id = "outcome_metric_short") %>%
#   # Now list only scenario
#   split(., .$case) 
# 
# 
# # Put together the different scenarios
# impact_mortality_comparative <- list()
# 
# for (r in c("2019", "whoaqg21")){ 
#   # Substract the impacts for the scenarios
#   impact_mortality_comparative[[paste0(r, "_whoaqg21")]] <- 
#     dplyr::left_join(impact_mortality_edited[[r]],
#                      impact_mortality_edited[["whoaqg21"]][c("rr_id", "ci", "impact", "impact_rounded" ,"outcome_metric_short", "exp")], 
#                      by = c("outcome_metric_short", "rr_id", "ci"), 
#                      suffix = c("_ref", "_whoaqg21")) %>%
#     dplyr::mutate(ref = r,
#                   impact_diff = impact_ref - impact_whoaqg21,
#                   impact_rounded_diff = impact_rounded_ref - impact_rounded_whoaqg21)
#   }
# 
# impact_mortality <- 
#   impact_mortality_comparative %>%
#   dplyr::bind_rows(.) %>%
#   # Remove non relevant columns
#   dplyr::select(-case, -rr_ci) %>%
#   
#   # Pivot wider CI
#   tidyr::pivot_wider(
#     values_from = c(rr, rr_forPaf, paf,
#                     impact_ref, impact_whoaqg21, impact_diff,
#                     impact_rounded_ref, impact_rounded_whoaqg21, impact_rounded_diff), names_from = ci) %>%
#   # Paste the CIs
#   dplyr::mutate(
#     rr_meanCI = paste_round_CI(rr_mean, rr_lowci, rr_highci, 3),
#     impact_ref_meanCI = paste_round_CI(impact_ref_mean, impact_ref_lowci, impact_ref_highci, 3),
#     impact_whoaqg21_meanCI = paste_round_CI(impact_whoaqg21_mean, impact_whoaqg21_lowci, impact_whoaqg21_highci, 0),
#     impact_diff_meanCI = paste_round_CI(impact_diff_mean, impact_diff_lowci, impact_diff_highci, 0),
#     # bhd as NA just to match with structure of morbidities
#     bhd = NA) %>%
# 
#     
#   # Left join to add further information on RR
#   dplyr::left_join(., rr_data, 
#                    by = c("info_pollutant" = "pollutant", "rr_id", "rr_increment",
#                           paste0("rr_", c("mean", "lowci", "highci"))),
#                    relationship = "many-to-one")%>%
#   # Change outcome_id to ensure match with codebook
#   dplyr::mutate(
#     outcome_id = ifelse(outcome_metric_short %in% "yll",
#                         gsub("premature deaths", "yll", outcome_id),
#                         outcome_id)) %>%
#   # Order columns 
#   dplyr::select(info_pollutant, ref, outcome_id, rr_source, 
#                 term, bhd, rr_meanCI, 
#                 contains("impact_diff_meanCI"),
#                 contains("impact_ref_meanCI"), 
#                 impact_whoaqg21_meanCI,
#                 everything()) %>%
#   # Order rows by label
#   dplyr::arrange(desc(info_pollutant), ref, outcome_id, rr_source)

```


## Comparison

```{r comparison singlebhd_rr}
# Test delta comparison function with fake values
comparison_delta_singlebhd_rr <-
  bestcost::compare_health_singlebhd_rr(
    comparison_method = "delta",
    exp_1 = 8.85, 
    exp_2 = 6,
    cutoff = 5,    
    bhd_1 = 25000,
    bhd_2 = 25000,
    rr = c(1.118, 1.060, 1.179),
    rr_increment = 10, 
    erf_shape = "log_linear", 
    info_1 = "PM2.5_mortality_2010",
    info_2 = "PM2.5_mortality_2020")


# Test pif comparison function with fake values
comparison_pif_singlebhd_rr <-
  bestcost::compare_health_singlebhd_rr(
    comparison_method = "pif",
    exp_1 = 8.85,  
    exp_2 = 6,
    cutoff = 5,    
    bhd_1 = 25000,
    bhd_2 = 25000,
    rr = c(1.118, 1.060, 1.179),
    rr_increment = 10, 
    erf_shape = "log_linear", 
    info_1 = "PM2.5_mortality_2010",
    info_2 = "PM2.5_mortality_2020")


```


```{r comparison ar}
# Test delta comparison function with fake values
# No PIF option in ar
comparison_delta_singlebhd_ar <-
  bestcost::compare_health_ar(
    exp_1 = c(57.5, 62.5, 67.5, 72.5, 77.5),# Values as example provided by NIPH
    exp_2 = c(50, 55, 60, 65, 75), # Fake values
    pop_exp_1 = c(387500, 286000, 191800, 72200, 7700), # Values as example provided by NIPH
    pop_exp_2 = c(387500, 286000, 191800, 72200, 7700), # Fake values
    erf_c = "78.9270-3.1162*c+0.0342*c^2",
    info_1 = data.frame(pollutant = "road_noise", outcome = "highly_annoyance", year = 2020),
    info_2 = data.frame(pollutant = "road_noise", outcome = "highly_annoyance", year = 2022))




```


```{r comparison deaths lifetable}
 
comparison_delta_lifetable_rr <-
  bestcost::compare_deaths_lifetable_rr(
    comparison_method = "delta",
    exp_1 = 8.85, # Fake data just for testing purposes
    prop_pop_exp_1 = 1, # Fake data just for testing purposes
    exp_2 = 6, # Fake data just for testing purposes
    prop_pop_exp_2 = 1, # Fake data just for testing purposes
    cutoff = 5,   # PM2.5=5, WHO AQG 2021 
    rr = c(1.118, 1.060, 1.179),
    rr_increment = 10, 
    erf_shape = "log_linear",
    first_age_pop_1 = 0,
    last_age_pop_1 = 99,
    interval_age_pop_1 = 1,
    prob_natural_death_male_1 = lifetable_withPopulation[["male"]]$death_probability_natural,
    prob_natural_death_female_1 = lifetable_withPopulation[["female"]]$death_probability_natural,
    prob_total_death_male_1 = lifetable_withPopulation[["male"]]$death_probability_total,
    prob_total_death_female_1 = lifetable_withPopulation[["female"]]$death_probability_total,
    population_male_1 = lifetable_withPopulation[["male"]]$population, 
    population_female_1 = lifetable_withPopulation[["female"]]$population, 
    year_of_analysis_1 = 2019, 
    first_age_pop_2 = 0,
    last_age_pop_2 = 99,
    interval_age_pop_2 = 1,
    prob_natural_death_male_2 = lifetable_withPopulation[["male"]]$death_probability_natural,
    prob_natural_death_female_2 = lifetable_withPopulation[["female"]]$death_probability_natural,
    prob_total_death_male_2 = lifetable_withPopulation[["male"]]$death_probability_total,
    prob_total_death_female_2 = lifetable_withPopulation[["female"]]$death_probability_total,
    population_male_2 = lifetable_withPopulation[["male"]]$population, 
    population_female_2 = lifetable_withPopulation[["female"]]$population, 
    year_of_analysis_2 = 2021, 
    info_1 = input_data_mortality$pollutant[i],
    info_2 = input_data_mortality$pollutant[i], 
    min_age = 30,
    max_age = NULL)
    # max_age = if(is.na(input_data_mortality$max_age[i])) NULL else input_data_mortality$max_age[i])

comparison_pif_lifetable_rr <-
  bestcost::compare_deaths_lifetable_rr(
    comparison_method = "pif",
    exp_1 = 8.85, # Fake data just for testing purposes
    prop_pop_exp_1 = 1, # Fake data just for testing purposes
    exp_2 = 6, # Fake data just for testing purposes
    prop_pop_exp_2 = 1, # Fake data just for testing purposes
    cutoff = 5,   # PM2.5=5, WHO AQG 2021 
    rr = c(1.118, 1.060, 1.179),
    rr_increment = 10, 
    erf_shape = "log_linear",
    first_age_pop_1 = 0,
    last_age_pop_1 = 99,
    interval_age_pop_1 = 1,
    prob_natural_death_male_1 = lifetable_withPopulation[["male"]]$death_probability_natural,
    prob_natural_death_female_1 = lifetable_withPopulation[["female"]]$death_probability_natural,
    prob_total_death_male_1 = lifetable_withPopulation[["male"]]$death_probability_total,
    prob_total_death_female_1 = lifetable_withPopulation[["female"]]$death_probability_total,
    population_male_1 = lifetable_withPopulation[["male"]]$population, 
    population_female_1 = lifetable_withPopulation[["female"]]$population, 
    year_of_analysis_1 = 2019, 
    first_age_pop_2 = 0,
    last_age_pop_2 = 99,
    interval_age_pop_2 = 1,
    prob_natural_death_male_2 = lifetable_withPopulation[["male"]]$death_probability_natural,
    prob_natural_death_female_2 = lifetable_withPopulation[["female"]]$death_probability_natural,
    prob_total_death_male_2 = lifetable_withPopulation[["male"]]$death_probability_total,
    prob_total_death_female_2 = lifetable_withPopulation[["female"]]$death_probability_total,
    population_male_2 = lifetable_withPopulation[["male"]]$population, 
    population_female_2 = lifetable_withPopulation[["female"]]$population, 
    year_of_analysis_2 = 2021, 
    info_1 = NULL,
    info_2 = NULL, 
    min_age = 30,
    max_age = NULL)
```



# Export 

```{r eval=FALSE, include=FALSE}
write.csv2(lifetable_airqplus,
            "../testing/output/lifetable_airqplus_2019_ch.csv", 
            row.names = FALSE)
```
