---
title: "Demo_UBD_Policy"
author: "Axel Luyten"
output: html_document
---

```{r}
library(healthiar)
library(dplyr)

load("../testing/input/data/input_data_for_testing_Rpackage.RData")

# cat(paste(
#   "Impact attributable to PM2.5 exposure: ",
#   as.numeric(impact_pm_copd[["health_main"]]$impact_rounded[1]),
#   sep = "\n"
#   ))

# print(impact_pm_copd[["health_main"]]$impact_rounded[1])

airqplus_pm_copd <- airqplus_pm_copd |> 
  mutate(incidence = incidents_per_100_000_per_year/1E5*population_at_risk)

## Rename data variables
data_pm_copd <- airqplus_pm_copd
rm(airqplus_pm_copd)
data_pm_copd <- data_pm_copd |> select(mean_concentration, cut_off_value, incidence, relative_risk, relative_risk_lower, relative_risk_upper)

data_lifetable <- input_data_mortality

data_deaths <- airqplus_pm_deaths_yll

## Remove not needed variables
rm(list=setdiff(ls(), 
                c("data_pm_copd",
                  "data_lifetable",
                  "lifetable_withPopulation",
                  "data_deaths"
                ))
   )
                  
```


# Population-weighted mean exposure and (simple) relative risk

```{r}
data_pm_copd
```


```{r}

impact_pm_copd <- 
  attribute_health(
    exp_central = data_pm_copd$mean_concentration,         ## 8.85 um / m3
    cutoff_central = data_pm_copd$cut_off_value,           ## 5 ug / m3
    bhd_central = data_pm_copd$incidence,                  ## 30747
    rr_central = data_pm_copd$relative_risk,               ## 1.369
    rr_lower = data_pm_copd$relative_risk_lower,           ## 1.124
    rr_upper = data_pm_copd$relative_risk_upper,           ## 1.664
    erf_increment = 10, 
    erf_shape = "log_linear", 
    info = paste0("assessment_1_pm_copd")
  )

impact_pm_copd[["health_main"]]

# View(impact_pm_copd)
```



# Multiple input uncertainties & exposure-response function from GBD2019

```{r}

impact_pm_copd_gbd <- 
  attribute_health(
    exp_central = data_pm_copd$mean_concentration,         ## 8.85 um / m3
    cutoff_central = data_pm_copd$cut_off_value,           ## 5 ug / m3
    bhd_central = data_pm_copd$incidence,                  ## 30747
    rr_central = data_pm_copd$relative_risk,               ## 1.369
    erf_increment = 10, 
    erf_shape = "log_linear",
    
    ## Exposure-response function from GBD2019
    erf_eq_central = stats::splinefun(
      x = c(0, 5, 10, 15, 20, 25, 30, 50, 70, 90, 110, 130, 150, 200, 300, 400, 500, 600),
      y = c(1.000,1.046,1.089,1.129,1.168,1.204,1.238,1.357,1.453,1.533,1.607,1.680,1.751,1.909,2.052,2.098,2.143,2.189),
      method = "natural"
    ),
    
    ## Confidence intervals of input data
    exp_lower = data_pm_copd$mean_concentration - 1,
    exp_upper = data_pm_copd$mean_concentration + 1,
    cutoff_lower = data_pm_copd$cut_off_value - 1,
    cutoff_upper = data_pm_copd$cut_off_value + 1,
    bhd_lower = data_pm_copd$incidence - 5000,
    bhd_upper = data_pm_copd$incidence + 5000,
    info = paste0("assessment_2_pm_copd")
  )

impact_pm_copd_gbd[["health_main"]]

impact_pm_copd_gbd[["health_detailed"]][["raw"]]

```

# Lifetable approach: years of life lost (YLL)

The healthiar package follows the lifetable approach used in AirQ+, but provides
additional options

```{r}

impact_lifetable <-
  attribute_yll_from_lifetable(
    exp_central = data_lifetable$exp[2],                   ## Exposure CH 2019
    cutoff_central = data_lifetable$cutoff[2],
    rr_central = data_lifetable[2,"rr_central"], 
    rr_lower = data_lifetable[2,"rr_lower"], 
    rr_upper =data_lifetable[2,"rr_upper"], 
    erf_increment = 10, 
    erf_shape = "log_linear",
    
    ## Approach specifications
    approach_exposure = "single_year",
    approach_newborns = "without_newborns",
    year_of_analysis = 2019, 
    min_age = 20, max_age = 99,
    
    ## Lifetable data
    first_age_pop = 0, last_age_pop = 99,
    population_midyear_male = lifetable_withPopulation[["male"]]$population, 
    population_midyear_female = lifetable_withPopulation[["female"]]$population, 
    deaths_male = data_deaths[["pop"]]$number_of_deaths_male,
    deaths_female = data_deaths[["pop"]]$number_of_deaths_female
    )

## Total YLL impact
impact_lifetable[["health_main"]]$impact_rounded[1]

## YLL per year
impact_lifetable[["health_detailed"]][["step_by_step_from_lifetable"]]$lifeyears_nest[3]$total_NA_1_central_central_central

## YLL per year and age group
impact_lifetable[["health_detailed"]][["step_by_step_from_lifetable"]]$yll_nest[3]$total_NA_1_central_central_central
```


# Iteration over multiple geo units

Impacts can be calculated for multiple geo units (e.g. municipalities) and 
aggregated at a higher level (e.g. region)

Population-weighted mean exposure can be calculated from shape files 
(containing municipality borders) and raster air pollution data 
(e.g. netCDF files) and then used for impact calculation


```{r}

impact_iteration <- 
  attribute_health(
    exp_central = as.list(rnorm(100, mean = data_pm_copd$mean_concentration, sd = 2)),         
    exp_lower = as.list(rnorm(100, mean = data_pm_copd$mean_concentration - 1, sd = 2)),         
    exp_upper = as.list(rnorm(100, mean = data_pm_copd$mean_concentration + 1, sd = 2)),
    cutoff_central = data_pm_copd$cut_off_value,
    bhd_central = as.list(rnorm(100, mean = data_pm_copd$incidence, sd = 200)),
    rr_central = data_pm_copd$relative_risk,               
    rr_lower = data_pm_copd$relative_risk_lower,           
    rr_upper = data_pm_copd$relative_risk_upper,           
    erf_increment = 10, 
    erf_shape = "log_linear",
    ## geo ID's
    geo_id_raw = 1:1E2, 
    geo_id_aggregated = rep("CH", 1E2),
  )

## Aggregated impact
impact_iteration[["health_main"]]

## Impact per geo unit
impact_iteration[["health_detailed"]][["raw"]] |> filter(erf_ci == "central") |>  filter(exp_ci == "central")
```

# Monetize health impacts

Discounting using exponential and hyperbolic methods is implemented

```{r}

impact_pm_copd_monetized <-
  include_cost(
    output = impact_pm_copd,
    valuation = 10000,                                     # Value of life year (VOLY)
    approach_discount = "exponential",
    corrected_discount_rate = 0.03,
    time_period = 20
  )

## Monetized results are added in a new "folder" to existing results 
# View(impact_pm_copd_monetized)

## Monetized impact
impact_pm_copd_monetized[["cost_main"]]

```

# Monte Carlo simulation

```{r}

impact_pm_copd_monetized_with_uncertainty <-
  include_summary_uncertainty(
    results = impact_pm_copd_monetized,
    n_sim = 1000
    )

## Summary uncertainty confidence intervals added in new "folder"
# View(impact_pm_copd_monetized_with_uncertainty)

## Summary uncertainty
print("Main estimates: ")
impact_pm_copd_monetized_with_uncertainty[["health_main"]][["impact_rounded"]]
print("Estimates from summary uncertainty:")
round(as.numeric(impact_pm_copd_monetized_with_uncertainty[["uncertainty_main"]]))

## Detailed Monte Carlo simulation results
impact_pm_copd_monetized_with_uncertainty[["uncertainty_detailed"]][["raw"]]

```
