---
title: "documentation_AirQ+_and_GeLuft_approaches"
author: "Axel Luyten"
output: html_document
---

# Goal: 
Document the AirQ+ and GeLuft life table approaches in parallel for future reference

```{r Load data}
knitr::opts_knit$set(root.dir = getwd())
# load("../testing/comparison_lifetable_approaches/input_data_get_pop_impact.Rdata")
load("../testing/comparison_lifetable_approaches/documentation_AirQ+_and_GeLuft_approaches.Rdata")
options(digits = 10)
pacman::p_load("dplyr", "purrr", "tidyr", "tibble")
```

# Setup

Starting point is a basic life table containing:
- mid-year population 
- deaths (from natural cause)
for each age from 0 - 99, 
and the population attributable fraction (calculated beforehand.
```{r}
head(lifetable)
```

In a first step, the probability of survival from start to end of a 
particular age, which is the same as from start of year i to start of year i+1,
is calculated as:
(mid-year pop - ( deaths / 2 ) ) / ( mid-year pop + (deaths / 2) )
Source: Miller, 2003, https://doi.org/10.1136/jech.57.3.200
```{r}
lifetable <- lifetable %>% 
  dplyr::mutate(prob_survival = ( population - ( deaths / 2 ) ) / ( population + ( deaths / 2 ) ), .after = deaths)
```

Next, probability of survival from start of age to mid-year is calculated as:
1 - ( ( 1 - survival probability ) / 2 )
which is equivalent to
1 - ( death probability / 2)
```{r}
lifetable <- lifetable %>% 
  dplyr::mutate(prob_survival_until_mid_year = 1 - ( ( 1 - prob_survival ) / 2 ), .before = prob_survival)
```

# Premature deaths

For the calculation of premature deaths attributable to the exposure the two 
approaches diverge:

GeLuft approach: 
Attributable deaths are calculated as:
Mid-year population * survival probability * PAF

AirQ approach:
Attributable deaths are the difference of the end-of-year populations of two scenarios:
Baseline scenario and impacted scenario.
To calculate the end-of-year population, we multiply the entry population
with
- the observed survival probability in case of the baseline scenario
- a modified survival probability in case of the impacted scenario

Entry population = mid-year population + (deaths / 2)
This implicitly assumes that deaths are distributed evenly throughout the year.

Modified survival probability for the impacted scenario is calculated as:
survival probability * (1 - PAF)
which can be expressed at
survival probability * population non-attributable fraction.

```{r}

# GeLuft
geluft <- lifetable %>% 
  mutate(premature_deaths_YOA = deaths * prob_survival * paf)

# AirQ+
airqplus_baseline <- lifetable %>% 
  
```




