# COMPARISON DIFFERENT LIFETABLE APPROACHES SINGLE-YEAR EXPOSURE CASE ##############################

Goal:
Compare different calculation pathways, that differ regarding 3 aspects:
1) Attribution approach: how the premature deaths attributable to 2019 air pollution are calculated (GeLuft vs AirQ+)
2) Projection approach: how these premature deaths are projected over time (Geluft vs AirQ+)
3) Death probability: whether total or natural death probabability is used for population projection

As we have 2 options for each of the 3 aspects, we end up with 2 x 2 x 2 = 8 calculation pathways.
The results of each pathway are named based on these options: the naming template is

attr_xxx_proj_xxx_prob_xxx

- e.g. a pathway that follows the GeLuft attribution approach, the AirQ+ projection approach and natural
death probability for the population projection is named: attr_air_proj_ge_prob_nat

All pathways have the same calculation basis: 2019 mid-year population, 2019 survival probabilities, 2019 deaths

```{r Load}
knitr::opts_knit$set(root.dir = getwd())
load("../testing/comparison_lifetable_approaches/input_data_get_pop_impact.Rdata")
options(digits = 15)

pacman::p_load("dplyr", "purrr", "tidyr", "tibble")

input_with_risk_and_pop_fraction <-
  input_with_risk_and_pop_fraction %>%
  filter(erf_ci == "central") %>%
  relocate(lifetable_with_pop_nest, .before = 1) %>%
  filter(sex == "male" | sex == "female")

```
This is the input data as it appeared at the start of "get_pop_impact()" after the call to "attribute_yll_from_lifetable"


## POPULATION SETUP
```{r Prepare lifetable}

pop <- input_with_risk_and_pop_fraction %>%
  dplyr::mutate(
    lifetable_with_pop_nest =
      lifetable_with_pop_nest %>%
      purrr::map(
        function(.x){
          .x <- .x %>%
            select(age, age_end, prob_natural_death, prob_total_death, deaths, population) %>%
            rename(!!paste0("population_",year_of_analysis) := population) %>%
            mutate(!!paste0("population_",year_of_analysis,"_entry") := !!sym(paste0("population_",year_of_analysis)) + (deaths / 2), .before = !!paste0("population_",year_of_analysis)) %>%
            mutate(prob_survival_natural = 1 - (deaths / !!sym(paste0("population_",year_of_analysis,"_entry"))), .after = deaths) %>% # probability of survival from start of year i to start of year i+1 (entry to entry)
            mutate(prob_survival_until_mid_year_natural = 1 - ((1 - prob_survival_natural) / 2), .after = deaths) %>%  # mutate(prob_survival_based_on_mid_year_pop = 1 - (deaths / !!sym(paste0("population_",year_of_analysis))), .after = prob_survival) %>% 
            mutate(deaths_total = population_2019 * prob_total_death, .before = deaths) %>% 
            mutate(prob_survival_total = 1 - (deaths_total / population_2019_entry), .after = deaths) %>% 
            mutate(prob_survival_until_mid_year_total = 1 - ((1 - prob_survival_total) / 2), .after = deaths) %>% 
            mutate(prob_survival_natural_from_hazard_rate = ( 2 - prob_natural_death ) / (2 + prob_natural_death ), .after = prob_survival_natural) %>% 
            mutate(prob_survival_natural_from_death_rate = ( 2 - (deaths / !!sym(paste0("population_",year_of_analysis,"_entry" )))) / (2 + (deaths / !!sym(paste0("population_",year_of_analysis,"_entry" )))), .after = prob_survival_natural )
          }
      )
    , .before = 1)

# Get difference in survival probabilities (Prob. survival inputted - prob. survival calculated)
diff_prob_survival_natural <- tibble(
  survival_prob_natural_geluft = 1 - pop$lifetable_with_pop_nest[[1]]$prob_natural_death,
  survival_prob_natural_airqplus = pop$lifetable_with_pop_nest[[1]]$prob_survival_natural,
  diff_abs = abs( ( 1 - pop$lifetable_with_pop_nest[[1]]$prob_natural_death) - pop$lifetable_with_pop_nest[[1]]$prob_survival_natural),
  diff_as_percent_of_input_survival_prob = diff_abs / ( 1- pop$lifetable_with_pop_nest[[1]]$prob_natural_death) * 100)
```
There is already a difference in survival probabilities at the start of calculations (see "diff_prob_survival_natural"):
- For ages 1 - 80 the difference is < 0.1%
- For ages 80 - 90 the difference is between 0.1% & 1%
- For ages 90+ the differences get pretty big

"prob_natural_death" comes from lifetable_withPopulation

To remove this possible source of the diverging results,
the next calculations will use all the same survival probabilities ("prob_survival_natural", i.e. the ones
calculated in the chunk above).

```{r Add PAF & modification factor and modified survival probabilities}
pop <-
  pop %>%
  dplyr::mutate(beta =
                  log(rr)/erf_increment,
                .after = rr) %>%
  dplyr::mutate(modification_factor = exp(beta * (cutoff - exp)), .after = beta) %>% 
  mutate(modification_factor_test = 1 / rr_conc)

pop <- pop %>%
  # Add the modification factor to the nested tibble "lifetable_with_pop_nest" using pmap()
  mutate(lifetable_with_pop_nest =
           pmap(
             list(lifetable_with_pop_nest, modification_factor),
             function(lifetable_with_pop_nest, modification_factor){
               lifetable_with_pop_nest <- lifetable_with_pop_nest %>%
                 mutate(modification_factor = modification_factor, .after = age_end)
             }
           )) %>% 
  # Add the PAF to the nested tibble "lifetable_with_pop_nest" using pmap()
  mutate(lifetable_with_pop_nest =
           pmap(
             list(lifetable_with_pop_nest, pop_fraction),
             function(lifetable_with_pop_nest, pop_fraction){
               lifetable_with_pop_nest <- lifetable_with_pop_nest %>% 
                 mutate(paf = pop_fraction, .after = modification_factor)
             })
         )

pop <- pop %>%
        dplyr::mutate(
          lifetable_with_pop_nest =
            lifetable_with_pop_nest %>%
            purrr::map(
              function(.x){
                .x <- .x %>%
                  mutate(hazard_rate_natural_modified = modification_factor * deaths / !!sym(paste0("population_",year_of_analysis)), .after = deaths) %>% # Hazard rate for calculating survival probabilities
                  mutate(prob_survival_natural_modified = (2 - hazard_rate_natural_modified) / (2 + hazard_rate_natural_modified), .after = deaths) %>%
                  mutate(prob_survival_until_mid_year_natural_modified = 1 - ((1 - prob_survival_natural_modified) / 2), .after = deaths) %>%
                  mutate(hazard_rate_total_modified = modification_factor * deaths_total / !!sym(paste0("population_",year_of_analysis)), .after = deaths) %>% 
                  mutate(prob_survival_total_modified = (2 - hazard_rate_total_modified) / (2 + hazard_rate_total_modified), .after = deaths) %>%
                  mutate(prob_survival_until_mid_year_total_modified = 1 - ((1 - prob_survival_total_modified) / 2), .after = deaths) %>%
                  mutate(prob_survival_natural_difference = prob_survival_natural_modified - prob_survival_natural, .after = prob_survival_natural) %>%
                  mutate(prob_survival_until_mid_year_natural_difference = prob_survival_until_mid_year_natural_modified - prob_survival_until_mid_year_natural, .before = prob_survival_natural_difference)
                  }
            )
        , .before = 1)
```
1 / rr_conc = modification_factor (this allows to circumvent the use of beta)

## GET IMPACT YEAR OF SINGLE YEAR EXPOSURE #########################################################

### AirQ+ APPROACH DIRECT ##########################################################################

```{r Calculate premature deaths directly}
pop <- pop %>%
        dplyr::mutate(
          attr_air =
            lifetable_with_pop_nest %>%
            purrr::map(
              function(.x){
                .x <- .x %>%
                  # Calculate premature deaths directly using 2019 entry pop
                  mutate(premature_deaths_2019 = 
                             population_2019_entry * prob_survival_natural_difference) %>% 
                  mutate(paf_from_mid_year_pop = premature_deaths_2019 / population_2019 / (1 - prob_survival_natural), .after = paf) %>% 
                  mutate(paf_from_entry_pop = premature_deaths_2019 / population_2019_entry / (1 - prob_survival_natural), .after = paf) %>% 
                  mutate(paf_1_minus_mod_factor = 1 - modification_factor, .after = paf_from_entry_pop) %>% 
                  mutate(premature_deaths_2019_paf_times_deaths = paf * deaths, .after = premature_deaths_2019) %>% 
                  mutate(premature_deaths_2019_using_paf_based_on_mod = paf_1_minus_mod_factor * deaths, .after = premature_deaths_2019) %>% 
                  mutate(deaths_from_entry_pop = population_2019_entry * (1 - prob_survival_natural), .after = deaths)

                
                  }
            )
        , .after = lifetable_with_pop_nest)
```
In the AirQ+ approach, calculations of premature deaths 2019 use the 2019 entry population.


AirQ+ APPROACH ORIGINAL (as a check that the direct approach gives correct results)
Calculate premature deaths as: modelled 2019 mid-year population - cutoff 2019 mid-year population
```{r Calculate premature deaths indirectly, eval=FALSE, include=FALSE}
pop <- pop %>%
        dplyr::mutate(
          attr_air_original =
            attr_air %>%
            purrr::map(
              function(.x){
                .x <- .x %>%
                  mutate(population_2019_cutoff = population_2019_entry * prob_survival_until_mid_year_natural_modified) %>% 
                  rename(population_2019_modelled = population_2019) %>% 
                  mutate(premature_deaths_2019_airqplus_original = 2 * (population_2019_cutoff - population_2019_modelled)) %>% 
                  select(age, age_end, population_2019_cutoff, population_2019_modelled, premature_deaths_2019_airqplus_original)
                }
              )
          , .after = attr_air)
```
I.e. results are the same as when using the direct calculation method.
Difference only after the 8th or 9th decimal, which is presumably a rounding error.

### GeLuft APPROACH ################################################################################

```{r}
pop <- pop %>% 
  dplyr::mutate(
    attr_ge =
      lifetable_with_pop_nest %>% 
      purrr::map(
        function(.x){
          .x <- .x %>% 
            mutate(premature_deaths_2019_based_on_input_prob_natural_death = population_2019 * prob_natural_death * paf) %>% # GeLuft approach using inputted prob of dying
            mutate(premature_deaths_2019 = population_2019 * (1 - prob_survival_natural) * paf) %>% # Geluft approach using calculated prob. of dying
            mutate(premature_deaths_2019_based_on_entry_pop = population_2019_entry * (1 - prob_survival_natural) * paf) %>%  # AirQplus approach
            mutate(premature_deaths_paf_times_deaths = paf * deaths) # Expected output

        }
      )
  , .after = attr_air)

```
In the GeLuft approach, calculations of premature deaths 2019 use the 2019 mid-year population,
but the survival probability that is applied is for start of 2019 to the end of 2019. This is a misalignment,
and introduces an error. 
The resulting absolute error in the premature deaths is smaller for ages when deaths are few (i.e. lower ages), but substantial
(several deaths) for higher ages, when deaths are higher.

If the mid-year 2019 population is to be used in calculations, the start-to-end of year survival probability has to 
be transformed to a mid-to-end of year survival probability! However, this seems artificial and 
unnecessarily complicated: first the start-to-end survival probability has to be calculated, and
then this has to be adjusted. Easier to calculate the entry population (= mid-year pop + half of 
deaths) and apply the start-to-end survival probability.


## PROJECT POPULATIONS #############################################################################

The "premature death populations" will be projected.

### AirQ+ APPROACH FOR POPULATION PROJECTION #######################################################

#### PROJECT USING NATURAL MORTALITY ###############################################################

The premature deaths attributed to exposure in the year 2019 are the 2020 entry population.
Natural mortality probability is used to project population.

```{r Project with natural mortality, include=FALSE}

years <- c(year_of_analysis:(year_of_analysis + (nrow(pop[["lifetable_with_pop_nest"]][[1]]) - 1)))
length_period <- length(years)

# Project premature deaths from AirQ+
pop <- pop %>% 
  mutate(attr_air_proj_air_prob_nat = attr_air %>% 
           purrr::map(function(.x){
             .x <- .x %>% 
               select(age, age_end, prob_survival_until_mid_year_natural, prob_survival_natural, population_2019, premature_deaths_2019 = premature_deaths_2019) %>% 
               mutate(pop_2020_entry = lag(premature_deaths_2019)) %>% 
               mutate(pop_2020 = pop_2020_entry * prob_survival_until_mid_year_natural)
             }
           )
         , .after = attr_air)

pop <- pop %>% 
  mutate(attr_air_proj_air_prob_nat = attr_air_proj_air_prob_nat %>% 
           purrr::map(function(.x){
             
             for (i in 2:(length_period - 1)) { # starts with 2 (corresponds to year 2020); ends with 99
               
                  cat("\nCalculate pop of year: ", years[i+1])

                  .x[(i + 1):length_period, paste0("pop_", years[i] + 1, "_entry")] <-
                    .x[i:(length_period - 1), paste0("pop_", years[i], "_entry")] * .x[i:(length_period - 1), "prob_survival_natural"]

                  .x[(i + 1):length_period, paste0("pop_", years[i] + 1)] <-
                    .x[(i + 1):length_period, paste0("pop_", years[i] + 1, "_entry")] * .x[(i + 1):length_period, "prob_survival_until_mid_year_natural"]
                }

                .x <- .x %>%
                  select(-contains("entry"))
                }
             )
         )


# Project premature deaths 2019 from GeLuft
pop <- pop %>% 
  mutate(attr_ge_proj_air_prob_nat = attr_ge %>% 
           purrr::map(function(.x){
             .x <- .x %>% 
               select(age, age_end, prob_survival_until_mid_year_natural, prob_survival_natural, population_2019, premature_deaths_2019 = premature_deaths_2019) %>% 
               mutate(pop_2020_entry = lag(premature_deaths_2019)) %>% 
               mutate(pop_2020 = pop_2020_entry * prob_survival_until_mid_year_natural)
             }
           )
         , .after = attr_ge)

pop <- pop %>% 
  mutate(attr_ge_proj_air_prob_nat = attr_ge_proj_air_prob_nat %>% 
           purrr::map(function(.x){
             
             for (i in 2:(length_period - 1)) { # starts with 2 (corresponds to year 2020); ends with 99
               
                  # cat("\nCalculate pop of year: ", years[i+1])

                  .x[(i + 1):length_period, paste0("pop_", years[i] + 1, "_entry")] <-
                    .x[i:(length_period - 1), paste0("pop_", years[i], "_entry")] * .x[i:(length_period - 1), "prob_survival_natural"]

                  .x[(i + 1):length_period, paste0("pop_", years[i] + 1)] <-
                    .x[(i + 1):length_period, paste0("pop_", years[i] + 1, "_entry")] * .x[(i + 1):length_period, "prob_survival_until_mid_year_natural"]
                }

                .x <- .x %>%
                  select(-contains("entry"))
                }
             )
         )
```

#### PROJECT USING TOTAL MORTALITY #################################################################

```{r Project with total mortality, include=FALSE}

years <- c(year_of_analysis:(year_of_analysis + (nrow(pop[["lifetable_with_pop_nest"]][[1]]) - 1)))
length_period <- length(years)

# Project premature deaths from AirQ+
pop <- pop %>% 
  mutate(attr_air_proj_air_prob_tot = attr_air %>% 
           purrr::map(function(.x){
             .x <- .x %>% 
               select(age, age_end, prob_survival_total, prob_survival_until_mid_year_total, population_2019, premature_deaths_2019 = premature_deaths_2019) %>% 
               mutate(pop_2020_entry = lag(premature_deaths_2019)) %>% 
               mutate(pop_2020 = pop_2020_entry * prob_survival_until_mid_year_total)
             }
           )
         , .after = attr_air)

pop <- pop %>% 
  mutate(attr_air_proj_air_prob_tot = attr_air_proj_air_prob_tot %>% 
           purrr::map(function(.x){
             
             for (i in 2:(length_period - 1)) { # starts with 2 (corresponds to year 2020); ends with 99
               
                  cat("\nCalculate pop of year: ", years[i+1])

                  .x[(i + 1):length_period, paste0("pop_", years[i] + 1, "_entry")] <-
                    .x[i:(length_period - 1), paste0("pop_", years[i], "_entry")] * .x[i:(length_period - 1), "prob_survival_total"]

                  .x[(i + 1):length_period, paste0("pop_", years[i] + 1)] <-
                    .x[(i + 1):length_period, paste0("pop_", years[i] + 1, "_entry")] * .x[(i + 1):length_period, "prob_survival_until_mid_year_total"]
                }

                .x <- .x %>%
                  select(-contains("entry"))
                }
             )
         )


# Project premature deaths 2019 from GeLuft
pop <- pop %>% 
  mutate(attr_ge_proj_air_prob_tot = attr_ge %>% 
           purrr::map(function(.x){
             .x <- .x %>% 
               select(age, age_end, prob_survival_total, prob_survival_until_mid_year_total, population_2019, premature_deaths_2019 = premature_deaths_2019) %>% 
               mutate(pop_2020_entry = lag(premature_deaths_2019)) %>% 
               mutate(pop_2020 = pop_2020_entry * prob_survival_until_mid_year_total)
             }
           )
         , .after = attr_ge)

pop <- pop %>% 
  mutate(attr_ge_proj_air_prob_tot = attr_ge_proj_air_prob_tot %>% 
           purrr::map(function(.x){
             
             for (i in 2:(length_period - 1)) { # starts with 2 (corresponds to year 2020); ends with 99
               
                  # cat("\nCalculate pop of year: ", years[i+1])

                  .x[(i + 1):length_period, paste0("pop_", years[i] + 1, "_entry")] <-
                    .x[i:(length_period - 1), paste0("pop_", years[i], "_entry")] * .x[i:(length_period - 1), "prob_survival_total"]

                  .x[(i + 1):length_period, paste0("pop_", years[i] + 1)] <-
                    .x[(i + 1):length_period, paste0("pop_", years[i] + 1, "_entry")] * .x[(i + 1):length_period, "prob_survival_until_mid_year_total"]
                }

                .x <- .x %>%
                  select(-contains("entry"))
                }
             )
         )
```


### GeLuft APPROACH FOR POPULATION PROJECTION ######################################################

#### PROJECT USING NATURAL MORTALITY #################################################################

The premature deaths attributed to exposure in the year 2019 are the 2020 mid year population.
Total mortality probability is used to project population.
```{r include=FALSE}

# Project premature deaths from AirQ+
pop <- pop %>% 
  mutate(attr_air_proj_ge_prob_nat = attr_air %>% 
           purrr::map(function(.x){
             .x <- .x %>% 
               select(age, age_end, prob_natural_death, population_2019, premature_deaths_2019 = premature_deaths_2019) %>% 
               mutate(pop_2020 = lag(premature_deaths_2019)) %>% 
               mutate(survival_probability_natural = 1 - prob_natural_death, .after = prob_natural_death)
             }
           )
         , .after = attr_air_proj_air_prob_nat)

pop <- pop %>% 
  mutate(attr_air_proj_ge_prob_nat = attr_air_proj_ge_prob_nat %>% 
           purrr::map(
             .,
             function(.x){
               
               for (i in 2:(length_period - 1)) { # starts with 2 (corresponds to year 2020); ends with 99
                 
                 cat("\nCalculate pop of year: ", years[i+1])
                 
                 .x[(i + 1):length_period, paste0("pop_", years[i] + 1)] <-
                   .x[i:(length_period - 1), paste0("pop_", years[i])] * .x[i:(length_period - 1), "survival_probability_natural"]
              
               }
               .x <- .x
             }
           )
  )


# Project premature deaths from GeLuft
pop <- pop %>% 
  mutate(attr_ge_proj_ge_prob_nat = attr_ge %>% 
           purrr::map(function(.x){
             .x <- .x %>% 
               select(age, age_end, prob_natural_death, population_2019, premature_deaths_2019 = premature_deaths_2019) %>% 
               mutate(pop_2020 = lag(premature_deaths_2019)) %>% 
               mutate(survival_probability_natural = 1 - prob_natural_death, .after = prob_natural_death)
             }
           )
         , .after = attr_ge_proj_air_prob_nat)

pop <- pop %>% 
  mutate(attr_ge_proj_ge_prob_nat = attr_ge_proj_ge_prob_nat %>% 
           purrr::map(
             .,
             function(.x){
               
               for (i in 2:(length_period - 1)) { # starts with 2 (corresponds to year 2020); ends with 99
                 
                 cat("\nCalculate pop of year: ", years[i+1])
                 
                 .x[(i + 1):length_period, paste0("pop_", years[i] + 1)] <-
                   .x[i:(length_period - 1), paste0("pop_", years[i])] * .x[i:(length_period - 1), "survival_probability_natural"]
              
               }
               .x <- .x
             }
           )
  )
```


#### PROJECT USING TOTAL MORTALITY ###############################################################
The premature deaths attributed to exposure in the year 2019 are the 2020 mid year population.
Total mortality probability is used to project population.
```{r include=FALSE}

# Project premature deaths from AirQ+
pop <- pop %>% 
  mutate(attr_air_proj_ge_prob_tot = attr_air %>% 
           purrr::map(function(.x){
             .x <- .x %>% 
               select(age, age_end, prob_total_death, population_2019, premature_deaths_2019 = premature_deaths_2019) %>% 
               mutate(pop_2020 = lag(premature_deaths_2019)) %>% 
               mutate(survival_probability_total = 1 - prob_total_death, .after = prob_total_death)
             }
           )
         , .after = attr_air_proj_air_prob_nat)

pop <- pop %>% 
  mutate(attr_air_proj_ge_prob_tot = attr_air_proj_ge_prob_tot %>% 
           purrr::map(
             .,
             function(.x){
               
               for (i in 2:(length_period - 1)) { # starts with 2 (corresponds to year 2020); ends with 99
                 
                 cat("\nCalculate pop of year: ", years[i+1])
                 
                 .x[(i + 1):length_period, paste0("pop_", years[i] + 1)] <-
                   .x[i:(length_period - 1), paste0("pop_", years[i])] * .x[i:(length_period - 1), "survival_probability_total"]
              
               }
               .x <- .x
             }
           )
  )


# Project premature deaths from GeLuft
pop <- pop %>% 
  mutate(attr_ge_proj_ge_prob_tot = attr_ge %>% 
           purrr::map(function(.x){
             .x <- .x %>% 
               select(age, age_end, prob_total_death, population_2019, premature_deaths_2019 = premature_deaths_2019) %>% 
               mutate(pop_2020 = lag(premature_deaths_2019)) %>% 
               mutate(survival_probability_total = 1 - prob_total_death, .after = prob_total_death)
             }
           )
         , .after = attr_ge_proj_air_prob_nat)

pop <- pop %>% 
  mutate(attr_ge_proj_ge_prob_tot = attr_ge_proj_ge_prob_tot %>% 
           purrr::map(
             .,
             function(.x){
               
               for (i in 2:(length_period - 1)) { # starts with 2 (corresponds to year 2020); ends with 99
                 
                 cat("\nCalculate pop of year: ", years[i+1])
                 
                 .x[(i + 1):length_period, paste0("pop_", years[i] + 1)] <-
                   .x[i:(length_period - 1), paste0("pop_", years[i])] * .x[i:(length_period - 1), "survival_probability_total"]
              
               }
               .x <- .x
             }
           )
  )
```



## COMPARE RESULTS #################################################################################

### CREATE OVERVIEW DATA FRAMES ##################################################################

#### PAF ###########################################################################################

```{r}
paf <- tibble(
  paf_geluft = pop$lifetable_with_pop_nest[[1]]$paf,
  paf_airqplus = pop$attr_air[[1]]$paf,
  diff_abs = round(abs(paf_geluft - paf_airqplus), digits = 7),
  diff_percentage_of_geluft_paf = round(abs(paf_geluft - paf_airqplus) / paf_geluft * 100, digits = 5),
  paf_airqplus_from_entry_pop = pop$attr_air[[1]]$paf_from_entry_pop)
```
It's possible to calculate the PAF in the AirQ+ approach using the equation:
PAF = abs(1 - modification_factor)!
Note that the PAF calculated using the formula:
paf = premature_deaths_2019_based_on_xxx_pop / population_2019 / (1 - prob_survival) is different for every year!!!

#### PREMATURE DEATHS ##############################################################################

```{r Compare premature deaths}

deaths <- tibble(
  age = pop$attr_air_proj_air_prob_tot[[1]]$age,
  deaths_airqplus = pop$attr_air_proj_air_prob_tot[[1]]$premature_deaths_2019,
  deaths_geluft = pop$attr_ge_proj_ge_prob_nat[[1]]$premature_deaths_2019,
  diff_abs = abs(deaths_airqplus - deaths_geluft),
  diff_as_percent_of_geluft = diff_abs / deaths_geluft * 100) #%>% 
  # mutate_all(., .funs = round, digits = 6)

cat("Sum premature deaths AirQ+: ", sum(deaths$deaths_airqplus))
cat("\nSum premature deaths GeLuft: ", sum(deaths$deaths_geluft))
cat("\nDifference: ", sum(deaths$deaths_airqplus) - sum(deaths$deaths_geluft))
cat("\nDifference as percent of GeLuft total: ", 
    (sum(deaths$deaths_airqplus) - sum(deaths$deaths_geluft)) / sum(deaths$deaths_geluft) * 100) 
```
Small difference in the first year.

#### YLL ###########################################################################################

```{r Compare age-specific yearly YLL}

yll_yoa <- tibble(age = pop$attr_air_proj_air_prob_tot[[1]]$age,
                  airqplus = pop$attr_air_proj_air_prob_nat[[1]]$premature_deaths_2019 / 2,
                  geluft_is = pop$attr_ge_proj_air_prob_tot[[1]]$premature_deaths_2019,
                  geluft_should = pop$attr_ge_proj_air_prob_tot[[1]]$premature_deaths_2019 / 2)
# In the year of analysis, with the GeLuft approach the number of premature deaths are the same as YLLs.
# This is correct for the population projections after the year of analysis, but not for the deaths,
# because we assume that on average people die in the middle of the year, so two people have to die
# for a "full" YLL.

yll_2020 <- tibble(
  age = pop$attr_air_proj_air_prob_tot[[1]]$age,
  attr_air_proj_air_prob_tot = pop$attr_air_proj_air_prob_tot[[1]]$pop_2020,
  attr_air_proj_air_prob_nat = pop$attr_air_proj_air_prob_nat[[1]]$pop_2020,
  attr_air_proj_ge_prob_tot = pop$attr_air_proj_ge_prob_tot[[1]]$pop_2020,
  attr_air_proj_ge_prob_nat = pop$attr_air_proj_ge_prob_nat[[1]]$pop_2020,
  attr_ge_proj_air_prob_tot = pop$attr_ge_proj_air_prob_tot[[1]]$pop_2020,
  attr_ge_proj_ge_prob_nat = pop$attr_ge_proj_ge_prob_nat[[1]]$pop_2020,
  attr_ge_proj_ge_prob_tot = pop$attr_ge_proj_ge_prob_tot[[1]]$pop_2020,
  attr_ge_proj_air_prob_nat = pop$attr_ge_proj_air_prob_nat[[1]]$pop_2020) #%>% 
  # mutate_all(., .funs = round, digits = 6)

yll_2050 <- tibble(
  age = pop$attr_air_proj_air_prob_tot[[1]]$age,
  attr_air_proj_air_prob_tot = pop$attr_air_proj_air_prob_tot[[1]]$pop_2050,
  attr_air_proj_air_prob_nat = pop$attr_air_proj_air_prob_nat[[1]]$pop_2050,
  attr_air_proj_ge_prob_tot = pop$attr_air_proj_ge_prob_tot[[1]]$pop_2050,
  attr_air_proj_ge_prob_nat = pop$attr_air_proj_ge_prob_nat[[1]]$pop_2050,
  attr_ge_proj_air_prob_tot = pop$attr_ge_proj_air_prob_tot[[1]]$pop_2050,
  attr_ge_proj_ge_prob_nat = pop$attr_ge_proj_ge_prob_nat[[1]]$pop_2050,
  attr_ge_proj_ge_prob_tot = pop$attr_ge_proj_ge_prob_tot[[1]]$pop_2050,
  attr_ge_proj_air_prob_nat = pop$attr_ge_proj_air_prob_nat[[1]]$pop_2050) #%>% 
  # mutate_all(., .funs = round, digits = 6)
```

```{r Compare total yearly YLL}
yll_difference <- abs(
  (pop$attr_air_proj_air_prob_nat[[1]] %>% select(contains("pop_"))) - (pop$attr_ge_proj_ge_prob_tot[[1]] %>% select(contains("pop_")))) 

yll_sum <- tibble(
  year = names(yll_difference),
  total_yll_airqplus_approach = colSums(pop$attr_air_proj_air_prob_nat[[1]] %>% select(contains("pop_")), na.rm = TRUE),
  total_yll_geluft_approach = colSums(pop$attr_ge_proj_ge_prob_tot[[1]] %>% select(contains("pop_")), na.rm = TRUE),
  diff_airqplus_minus_geluft = total_yll_airqplus_approach - total_yll_geluft_approach, 
  diff_as_percent_of_geluft = diff_airqplus_minus_geluft / total_yll_geluft_approach * 100) %>% 
  mutate_if(., is.numeric, round, digits = 4)
```

```{r Using natural vs total survival probability}

nat_vs_tot_survival_prob_airqplus <- tibble(
  year = names(pop$attr_air_proj_air_prob_tot[[1]] %>% select(contains("pop_"))),
  projection_with_survival_prob_natural = colSums(pop$attr_air_proj_air_prob_nat[[1]] %>% select(contains("pop_")), na.rm = TRUE),
  projection_with_survival_prob_total = colSums(pop$attr_air_proj_air_prob_tot[[1]] %>% select(contains("pop_")), na.rm = TRUE),
  diff_abs = projection_with_survival_prob_natural - projection_with_survival_prob_total,
  diff_as_percent_of_natural = diff_abs / projection_with_survival_prob_natural * 100) %>% 
  mutate_if(., is.numeric, round, digits = 4)
```

Other comparisons can be added below!
